Title

### 2023-06-12 main.tex
Arrrrgggg

@@

Since their inception, quantum computers were proposed as powerful tools for the simulation of quantum systems,
with a recent particular interest in simulating the evolution of open quantum systems, 
which are described by the theory of quantum channels~\cite{cleve,Zanetti,Xin,Wei}. \tbnote{Cita a Andrea}
{\color{purple} For example, this has been done using optical arrangements
to study the emergence of multipartite entanglement \cite{Andrea,Andrea_AD}.}
Among the various types of quantum channels for a system of qubits, 
Pauli channels hold special significance due to their simplicity 
and relevance in the context of quantum computing~\cite{Zbigniew,geometry}, 
as they serve as effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.

Additionally , we shall also work with parametrized quantum circuits, that is,  
quantum circuits in which some of the operations depend on variable parameters~\cite{cerezo}. 
These circuits play an important 
part in applications such as quantum machine learning~\cite{Benedetti}
and describing general quantum transformations dependent on parameters. Substantial research has been 
devoted to enhancing the efficiency of these circuits~\cite{Watanabe,Rasmussen}.

@@

Expanding beyond discrete Pauli channels,
we introduce the concept of Pauli dynamical maps, 
defined as a continuous parametrization of
$N$-qubit Pauli channels. 
We adapt the algorithm developed for Pauli channels 
to accommodate these dynamical maps by employing a 
parametrized quantum circuit. 
Furthermore, we contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2},
which outlines the types of transformations that 
can be done using a parametrized circuit with the condition that only one
 single-qubit operation in the circuit may depend on the parameter.
We explicitly find the mathematical conditions for these types of
transformations and conclude about which 
Pauli dynamical maps can be done with them.

>>>>

\cpnote{Porfa 3 propuestas de titulo y un intento de abstract. Ese es mas facil que la intro!
de neuvo, quizá vale la pena que te einspires en otros abstracts de PlosOne}

@@

Since their inception, quantum computers were proposed as powerful tools for the simulation of quantum systems,
with a recent particular interest in simulating the evolution of open quantum systems, 
which are described by the theory of quantum
channels~\cite{cleve,Zanetti,Xin,Wei}. \tbnote{Cita a Andrea}
{\color{purple} For example, this has been done using optical arrangements
to study the emergence of multipartite entanglement \cite{Andrea,Andrea_AD}.}
\cpnote{Se siente forzada. nos toca encontrar mas ejemplos e introducirla de
manera mas natural. Quizá mas adelante}
Among the various types of quantum channels for a system of qubits, 
Pauli channels hold special significance due to their simplicity 
and relevance in the context of quantum computing~\cite{Zbigniew,geometry}, 
\cpnote{Aca citar nuestros trabajos con Davalos. }
as they serve as effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.
\cpnote{Creo que la transición de general a particular va demasiado rapido. Quizá hacerle 
ver a Tomas y luego reescribirlo yo}

\cpnote{De nuevo una transicion muy abrupta. Para que ver los circuitos? Priero 
hablar de los circuitos, quizá una frase, luego hablar de los parametrizadso, 
Aca quiza citar a Barrero en innsbruk con sus vainas de enlazamiento}
Additionally, we shall also work with parametrized quantum circuits, that is,  
quantum circuits in which some of the operations depend on variable parameters~\cite{cerezo}. 
These circuits play an important 
part in applications such as quantum machine learning~\cite{Benedetti}
and describing general quantum transformations dependent on parameters. Substantial research has been 
devoted to enhancing the efficiency of these circuits~\cite{Watanabe,Rasmussen}.

@@

Expanding beyond discrete Pauli channels,
we introduce the concept of Pauli dynamical maps, 
defined as a continuous parametrization of
$N$-qubit Pauli channels. 
We adapt the algorithm developed for Pauli channels 
to accommodate these dynamical maps by employing a 
parametrized quantum circuit. 
Furthermore, we contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2},
which outlines the types of transformations that 
can be done using a parametrized circuit with the condition that only one
 single-qubit operation in the circuit may depend on the parameter.
We explicitly find the mathematical conditions for these types of
transformations and conclude about which 
Pauli dynamical maps can be done with them. 
\cpnote{Me gustaron mucho estos dos ultimos parrafos. Croe que se puede ir mencionando las secciones
y poner la info del siguiente parrafo aca. Ahora, no lo pongas a lo bestia, sino realmente
integrando e hilando las ideas. Si hay preguntas, me dices que tos.}
